---
title: ''
output: pdf_document
---
\section{Upscaling and NMR relaxometry of model process cheese}
\subsection{Introduction}
The basis of nuclear magnetic resonance spectroscopy (NMR) is the fact that atoms have magnetic fields characteristics. Subatomic particles, such as neutrons, electrons, and protons, revolve around their axis, which in particle physics is called spin. Atomic nuclei with an odd number of protons, e.g., 1H, have a total spin (I). Atoms with an even number of protons, e.g., C, have no total spin due to the pairing of the protons. A parallel orientation of the magnetic moment results in the energetically preferred orientation of it. The difference in occupation that occurs creates a magnetisation vector which is the basis of a successful NMR measurement [@Schuh1982].

The NMR measurements were used to investigate the mobile water phase of the processed cheese system at different process times. The interpretation of the relaxation times can determine the chemical and physical, bound or unbound state of 1H protons and thus of water.
1H nuclei from immobilised water have considerably shorter relaxation times than nuclei from the mobile water phase. This can be attributed to the interactions of the immobile protons with their environment, which are much more frequent than those of the mobile phase of the system. By measuring the decaying signal intensity over the relaxation time, a spectrum of the different water phases in the melted cheese system was obtained [@Hinrichs2004]. Studies on the water-binding capacity of protein microparticles using time-domain nuclear magnetic resonance were performed also by @Peters2016. Water immobilization by whey protein concentrate was investigated by NMR in @Hinrichs2004a.
NMR measurements on food and model systems thereof, especially low-resolution experiments on cheese, are a common practice[@Gotz2004]. @Chen2012 investigated the effect of different types and amounts of emulsifying salts on the chemical and physical properties of processed cheese samples. Furthermore, signal components were also be attributed to the fat protons. @Noronha2008c identified four stages of hydration and/or matrix development in the preparation of imitation cheese made from casein. Two stages could be attributed to hydrophilic interactions of caseins with the bulk as well as two later stages, where the interactions of proteins with fat dominated the matrix formation. @Hinrichs2007 investigated changes in water mobility during renneting or acidification of solutions from casein micelles, using low resolution NMR. Here, a method was presented to fit the signal to relaxation times of differently bound fractions of water - immobile, weakly mobile, mobile and very mobile protons from water were detected. In @Khanal2018, different low fat cheddar cheeses were investigated during ripening. Using low-field NMR, different stages of water mobility could be identified in samples containing alginate as additive.
Further use of time-domain or low-resolution NMR measurements can be found as well in composite science. @Besghini2019 present NMR measurements for the investigation of polymerization or crystallization kinetics in rubber. Gelation and sol-gel phase transition phenomena in non-biogenic, organic materials like Poloxamers are investigated via T2 relaxation by @Shaikhullina2020. @Testamanti2019 gives use of low-field or low-resolution magnetic resonance for the evaluation of reservoirs for the petroleum industry and is especially focussed on the provision of a regularization algorithm for the determination of T2 relaxation spectra from shells.
Determination of the T2 distribution from the decaying signal can be obtained by  the CONTIN Computer Program, where an inverse Laplace transformation of the signal is performed, in order to find the T2 distribution [@Moody2004, @Whittall1996, @Borgia1998, @Handling]. Another possibility to obtain the relaxation and diffusion distributions in two dimensions is the use of the Fredholm integral equation of the first kind [@Mitchell2012]. However, this can lead to a regularization bias, since the inverse Laplace transform represents an ill-posed problem [@Berman2013, @Giovannelli2015], especially for a multi-component environment as it is the case in processed-cheese samples. 
Fitting the envelope curve of the exponential decay with discrete parameters as in @Hinrichs2007 leads to unbiased T2 distributions, however only for the discrete parameters. Least-squares and linear programming algorithms can help to reduce the non-uniqueness of the fitted solution, meaning that the fit is not constrained by initially given discrete parameters and can therefore represent the spectrum in a more accurate way [@Whittall1989].

\subsection{Material and Methods}

\subsubsection{Preparation of cheese samples}
Composition of the cheese premix can be found in Chapter 3. Only samples from rennet casein were produced for the NMR measurements, since they appeared to deliver the most homogenous product samples. In order to speed up the analysis time, the model process cheese was processed in a 500g batch, the matrix was processed in a Vorwerk Thermomix processing machine. Samples were taken every five minutes and cooled at 4 C.
\subsubsection{NMR measurement}
The measurement was carried out in the sample tubes provided. The processed cheese sample was punched out with the open end of the sample tube and slightly compacted with a plastic rod to avoid air inclusions. The initial analysis was performed at 10°C using the NMR analyser mq20 minispec (Bruker Corporation , Billerica, USA). Each sample was measured in duplicate for different process times (0- 360 min, in 5 min steps).
Measurement parameters were adapted from @Hinrichs2007 

\subsubsection{Curve-fitting}
The envelope curve obtained by the decaying signal of the nuclear magnetig spins was fitted using the R Programming Environment. The curve was fitted using a non-linear least squares (NLS) algorithm, where the parameters were estimated in a two step fitting protocol (see code snippet and explanation below). 

\subsection{Results and Discussion}
```{r include=FALSE}
#library
library(tidyverse)
library(data.table)
library(plyr)
library(readr)
library(BBmisc)
library(stringr)
library(plot3D)
library(ggfortify)
library(ggforce)
library(reshape2)
library(mixtools)
library(pracma)
library(missMDA)
library(cluster)

#summarySE
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summarized
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```

```{r include=FALSE}
#T2 distributions
# data chapter V
## Import NMR data

# go through all files in the folder 
files <- list.files(path="~/Desktop/PhD/data/Rstudio/Rdata_diss/thesis/NMR_fat", pattern="*.dps", full.names=TRUE, recursive=FALSE)

# read them and merge them into a single table
table_list <- lapply(files, function(x) {
  x <- read.table(x, sep="\t", header=F)
  colnames(x) <- c("count", "x", "y")
  x
})

NMR_list <- table_list
ID <- list.files(path="~/Desktop/PhD/data/Rstudio/Rdata_diss/thesis/NMR_fat", pattern="*.dps", full.names=F)
pr.ti <- str_split_fixed(ID, "[:digit:].dps", 2) %>% as.data.frame()
pr.ti$V1 <- str_split_fixed(pr.ti$V1, "_[:digit:]", 2) 
pr.tim <- pr.ti$V1 
pr.tim <- str_split_fixed(pr.tim, "_", 3) %>% as.data.frame()
pr.tim$V2 <- revalue(pr.tim$V2, c("DB"="2"))
NMR.ID <- mutate(pr.tim, ID = paste(pr.tim$V1, pr.tim$V2, sep = "_"))
NMR.ID <- NMR.ID[1:132,4]
names(NMR_list) <- NMR.ID

NMR_short <- function(xlist){
  xlist <- xlist[][1:2000, ]
}
NMR_list <- lapply(NMR_list, NMR_short)

NMRfit3 <- function(xlist){
  t <- xlist[["x"]]
  y <- xlist[["y"]]
  p0 <- c(-.01, -10, -100)
  modnew <- mexpfit(t, y, p0)
  fit1 <- nls(y ~ cbind(exp(-(t/(2*k1))^2), exp(-t/k2), exp(-t/k3)), algorithm = "plinear", data = xlist,
              start = list(k1 = .01, k2 = 10, k3= 100), nls.control(maxiter = 500, warnOnly = TRUE))
  k1_predict <-summary(fit1)$coefficients[1,1]
  k2_predict <-summary(fit1)$coefficients[2,1]
  k3_predict <-summary(fit1)$coefficients[3,1]
  fo <- y ~ f1*exp(-(t/(2*k1))^2)+f2*exp(-t/k2)+f3*exp(-t/k3);
  f1_predict <- modnew$a[1]
  f2_predict <- modnew$a[2]
  f3_predict <- modnew$a[3]
  fit2 <- nls(fo, data = xlist, 
              start = list(k1 = k1_predict, k2 = k2_predict, k3 = k3_predict, 
                           f1 = f1_predict, f2 = f2_predict, f3 = f3_predict), nls.control(maxiter = 500, warnOnly = TRUE))
  fit.param <- as.data.frame(fit2$m$getPars())
  fit.param}


fit.full3 <- lapply(NMR_list, NMRfit3)
```

```{r include=FALSE}
fit3res <- do.call("cbind", fit.full3)
colnames(fit3res) <- NMR.ID
fit3res <- as.data.frame(t(fit3res))
NMR.time <- str_split_fixed(NMR.ID, "min", 2) %>% as.data.frame()
timeNMR <- NMR.time$V1
timeNMR <- gsub(",",".",timeNMR)
fit3res <- bind_cols(timeNMR, fit3res)
colnames(fit3res)[1] <- "time"
fit3res$time <- as.numeric(fit3res$time)
fit3res <- arrange(fit3res, time)
fit3res <- fit3res[c(1:32, 36:128),] #outlier and last value exclusion by Grubb's test

longfit3 <- fit3res %>% pivot_longer(., c(k1, k2, k3, f1, f2, f3), 
                                     names_to = "parameter", values_to = "value")
T2 <- filter(longfit3, str_detect(parameter, "k"))
T2mean <- summarySE(data = T2, measurevar = "value", groupvars = c("time", "parameter") )
T21 <- filter(T2mean, str_detect(parameter, "1"))
T2f3 <- filter(T2mean, str_detect(parameter, c("2", "3")))
T2f <- filter(T2mean, str_detect(parameter, "2"))
T23 <- filter(T2mean, str_detect(parameter, "3"))

plot.T2 <- function(df){ggplot(df, mapping = aes(x = time, y = value, color = parameter, group = parameter))+ geom_point(aes(shape=parameter))+ theme_bw() + scale_y_log10()+ theme(legend.position = "none")+
    geom_errorbar(aes(ymin=value-se, ymax=value+se),linetype=1 , color= "black", width=5) + 
    geom_smooth(method = lm, se = FALSE)+xlab("process time [min]")+ylab("T2 [ms]")}

T2f3.p <- plot.T2(T2f3)
```

\subsubsection{NMR measurements}

```{r , echo=FALSE, warning=FALSE}
T2dist <- filter(longfit3, str_detect(parameter, "f")) #c("f2","f3")
T2meandist <- summarySE(data = T2dist, measurevar = "value", groupvars = c("time", "parameter") )
plot.T2dist <- function(df){ggplot(df, mapping = aes(x = time, y = value, color = parameter, group = parameter))+ geom_smooth(method=lm, se=FALSE)+
    geom_point(aes(shape=parameter))+ theme_bw() + 
    geom_errorbar(aes(ymin=value-se, ymax=value+se),linetype=1 , color= "black", width=5) +
    xlab("process time [min]")+ylab("fraction [%]")}
p.T2meandist <- plot.T2dist(T2meandist)
```

```{r , echo=FALSE, warning=FALSE, fig.cap="Development of the fractions of T2 relaxation times of fatty phase (red) and modile water phase (blue) with respective linear model fit: fraction of bound fat increases, while fraction of mobile water decreases."}
p.T2meandist
```

The biggest fraction of the model cheese matrix is the dispersed phase, as represented by Fig.xx. Also the volume fraction of the fatty phase increases, which is consistent with the data obtained by @Vollmer2021 and chapters 4 and 5 of the present study. Also, the amount of mobile water protons decreases, which is also in conclusion with previous findings.

```{r , echo=FALSE, warning=FALSE, fig.cap="Development of T2 relaxation times of fatty phase (red) and modile water phase (blue) with respective linear model fit: Increase in water mobility and decrease of mobility of the fatty phase" }
T2f3.p
```
Fig.xx shows the development of T2 distributions for the detected fatty- and mobile-water-phase. No changes were detectable in the immobile-water-phase (data not shown). 
Analogous to the distribution of the relaxation times (Gig.xx), the relaxation time for the watery phase shows an overall increase over the process time, whereas the the T2 relaxation time for the fatty phase decreases. A decrease in T2 relaxation time indicates a stronger interaction of the magnetized protons with their environment, here the gel matrix. An increase in T2 relaxation represents a lesser interaction. Hence it can be concluded, that over the course of processing of the model processed cheese matrix, fat gets bound more tightly by the matrix, whereas mobile water is released. 

The T2 relaxation time data was analyzed using a linear model, accuracy of the fit was determined by an  R^2 of 0.93:
```{r, echo=FALSE}
XX <-lm(value ~ parameter + time, data = T2f3)
summary(XX) 
```

\subsubsection{Protein concentration in the serum phase}

```{r include=FALSE}
pc.nmr <- read_csv2("~/Desktop/PhD/data/Rstudio/Rdata_diss/thesis/offline_serum_hplc.csv")
pc.nmr.time <- str_split_fixed(pc.nmr$sm, "_", 3) %>% as.data.frame()
pc.nmr.time <- str_split_fixed(pc.nmr.time$V2, "min", 2) %>% as.data.frame()
pc.nmr <- bind_cols(pc.nmr.time, pc.nmr[,2:6])

pc.nmr.l <- pivot_longer(pc.nmr, c(kap, as2, as1, bet, TP), names_to = "protein", values_to = "amount")
pc.nmr.l$amount <- pc.nmr.l$amount*5 #dilution factor HPLC
mean.pc.nmr <- summarySE(pc.nmr.l, measurevar = "amount", groupvars = c("V1", "protein"))
mean.pc.nmr$V1 <- as.numeric(mean.pc.nmr$V1)
mean.pc.nmr <- arrange(mean.pc.nmr, V1) %>% filter(str_detect(protein,"TP"))
pd = .5

#TP from chapter 3
file_list <- list.files("~/Desktop/PhD/data/Rstudio/Rdata_diss/thesis/HPLC_raw", recursive = T, full.names = T)

data_list <- lapply(file_list, function(x) {
  x <- read_csv2(x, col_names = T)
  x})

df <- bind_rows(data_list)
HPLC_TP <- df
kap <- HPLC_TP$kap 
as1 <- HPLC_TP$as1
as2 <- HPLC_TP$as2
bet <- HPLC_TP$bet
TP <- kap+as1+as2+bet %>% as.numeric()

HPLC_TP <- bind_cols(HPLC_TP, TP)
colnames(HPLC_TP)[11] <- "TP"

HPLCtp<- pivot_longer(HPLC_TP, c(kap, as2, as1, bet, TP), names_to = "protein", values_to = "amount")

calculate_HPLC <- function(data=NULL, dil.Volume){
  cream <- filter(data, str_detect(tm, "Cream")) %>% mutate(., value = amount*0.5)
  pellet <- filter(data, str_detect(tm, "Pellet")) %>% mutate(., value = amount*5*dil.Volume)
  serum <- filter(data, str_detect(tm, "Serum")) %>% mutate(., value = amount*10)
  wash <- filter(data, str_detect(tm, "Waschung")) %>% mutate(., value = amount*1)
  
  calc <- bind_rows(cream, pellet, serum, wash)
  calc <- select(calc, -amount)
  
  return(calc)
}

HPLC.TP <- calculate_HPLC(HPLCtp, dil.Volume = 5)

HPLCall <- summarySE(HPLC.TP, measurevar = "value", groupvars = c("source", "tm", "sm", "protein", "mea.type", "data.type"))
TPs3 <- filter(HPLCall, str_detect(tm, "Serum"))
TPs3 <- filter(TPs3, str_detect(protein, "TP"))
TPs3 <- TPs3[1:10, c(3,4,7:11)]
TPs3$sm <- revalue(TPs3$sm, c("A"="0", "B"="8", "C"="45", "D"="60", "E"="85", "F"="105", "G"="140", "H"="160", "J"="180", "K"= "200"))
TPs3$sm <- as.numeric(TPs3$sm)

colnames(TPs3) <- paste(colnames(mean.pc.nmr))
mean.pc.nmr <- bind_rows(mean.pc.nmr, TPs3)
nmr.pc <- ggplot(mean.pc.nmr, mapping = aes(x = V1, y = amount, color=N, group=N)) + geom_point()+ geom_smooth(method=lm,se=FALSE, linetype=2)+theme_bw()+theme(legend.position = "none")+
      geom_errorbar(aes(ymin=amount-se, ymax=amount+se),linetype=1 , color= "black", width=5) + 
    xlab("process time [min]")+ylab("protein concentration [mg/ml]")
```

```{r , echo=FALSE, warning=FALSE, fig.cap="Development of measured protein concentration in the centrifugationally separated serum phase (500g) over the course of processing, with a linear fit (dashed line), compared to the development of the total protein concentration in the serum phase processed as a batch in a rheometer (see chapter 3) and centrifugationally separated at 6000g (blue)"}
nmr.pc
```
FIg.xx shows the development of the total protein concentration of the processed cheese matrix used for the NMR measurements, compared to the total protein concentration in the serum as presented in chapter 3.
The difference in the measured samples lies in the centrifugational separation speed (6000g or 500g respectively) as well as in the mode of preparation (batch, or continous upscaled process). Overall the protein concentrations measured in both preparation modi are in the same range of ~30-50 mg/ml. Also, both measurements show a general trend of a decreasing concentration of soluble protein during processing.
Interestingly, the separation at 500g (black) gives a more dynamic representation of the changes in the soluble protein concentration, as explained in more detail in the following section:
The initial increase in the protein concentration can be explained by the dissociation of the casein micelle, induced by the melting salts. After reaching a maximum concentration, the amount of protein detectable in the serum phase decreases up to a processing time of ~145 minutes to a minimum value of ~28mg/ml. Towards the end of processing, an increase in soluble protein was measured. 
EXPLANATION

\subsubsection{Particle size distribution in the serum phase of the upscaled, continous process}

```{r include=FALSE}
pgv.nmr <- read_csv2("~/Desktop/PhD/data/Rstudio/Rdata_diss/thesis/serum_offline_500g.csv")
```

\subsubsection{"Offline" Rheology of continous process}
```{r include=FALSE}
rheo.off<- read.csv("~/Desktop/PhD/data/Rstudio/Rdata_diss/thesis/as_20180119_LC_CP-dV.csv")
rheo.off.norm <- rheo.off[,-1]

col.m <- colMeans(rheo.off.norm) %>% as.data.frame()
col.m <- col.m[1:13,]
time.offline <- c(300/60, 1500/60, 3000/60, 4200/60, 4800/60, 5400/60, 6000/60, 7800/60, 9000/60, 10200/60, 11400/60, 13200/60, 14400/60)

offline <- bind_cols(time.offline, col.m)
colnames(offline) <- c("time", "viscosity")
offline <- offline[c(1:4,6:9,11,12),]
p.offline <- ggplot(offline, mapping = aes(x=time, y=viscosity))+geom_point()+theme_bw()+
  theme(legend.position = "none")+ ylab("apparent viscosity [Pa*s]")+ xlab("time [min]")
```


```{r, echo=FALSE, warning=FALSE, fig.cap="Rheological profile of the samples prepared for NMR measurements: measured mean viscosity of the samples processed continously in the Thermomix, measured with a cone-plate geometry"}
p.offline+geom_line(linetype=2)
```

\subsection{Conclusion and Outlook}

Further insight towards the aggregation phenomena of soft-solids like processed or cream cheese could be obtained via pulsed field gradient-nuclear magnetic resonance (PFG-NMR). @LeFeunteun2012 distinguished dissolved casein monomers besides casein particles during the rennet coagulation of highly concentrated casein suspensions. The concentration of monomers increased during the experiments, while the amount of casein particles decreased. @Salami2013 also permormed PFG-NMR measurements to measure the diffusion of non-micellar phosphocaseinate and sodium caseinate preparations in environments with different Polyethylene glycols.