---
title: ''
output: pdf_document
---
```{r}
# data provision for pca

summary_rheo <- sum_t.v

dM_product <- plot.dM
dM_cream <- plot.dM.cream
pH_process <- plot.pH

HPLC_product <- HPLC.full[,c(1:4,9)]
HPLC_product$sm <- as.character(HPLC_product$sm)
HPLC_product$sm <- revalue(HPLC_product$sm, c("0"="A", "8"="B", "25"="C", "33"="D", "45"="E", "70"="F", "100"="G", "125"="H", "130"="J",  "145"="K"))
HPlC_product_pca <- HPLC_product %>% pivot_wider(., id_cols = sm, values_from = value, names_from = c(source, tm, protein), names_sep = "_")

pgv_cream <- dens2cream
pgv_pellet <- dens2pellet
pgv_serumUZ <- dens2serumUZ
pgv_serumZF <- dens2serumZF
pgv_colloid <- dens2coll
colnames(pgv_colloid) <- collmins$tm
cm <- collmins$time %>% as.numeric()
cm <- as.data.frame(t(cm))
colnames(cm) <- collmins$tm
pgv_colloid <- bind_rows(cm, pgv_colloid)
colnames(pgv_colloid) <- collmins$tm

colloid_rheo <- c_rheo
HPLC_colloid <- HPLC_coll


```

```{r}
# data restructuring colloid
size1_coll <- pgv_colloid[c(1,5),]
size2_coll <- pgv_colloid[6,]
sizes_coll <- bind_rows(size1_coll, size2_coll)
colnames(sizes_coll) <- collmins$tm

sizes_3oSnoG <- sizes_coll[-1,1:10]
colnames(sizes_3oSnoG) <- LETTERS[c(1:8,10,11)]
sizes_3oSZF <- sizes_coll[, 11:20]
colnames(sizes_3oSZF) <- LETTERS[c(1:8,10,11)]
sizes_3mSnoG <- sizes_coll[,21:30]
colnames(sizes_3mSnoG) <- LETTERS[c(1:8,10,11)]
sizes_3mSZF <- sizes_coll[,31:40]
colnames(sizes_3mSZF) <- LETTERS[c(1:8,10,11)]
sizes_1mSnoG <- sizes_coll[,41:48]
colnames(sizes_1mSnoG) <- LETTERS[c(1:5,8,10,11)]
sizes_1mSZF <- sizes_coll[,49:56]
colnames(sizes_1mSZF) <- LETTERS[c(1:5,8,10,11)]

## NA cols for missing values:
F <- c(100, NA, NA)
G <- c(120,NA, NA)
sizes_1mSnoG <- bind_cols(sizes_1mSnoG, F, G)
colnames(sizes_1mSnoG)[9:10] <- c("F", "G")
sizes_1mSZF <- bind_cols(sizes_1mSZF, F, G)
colnames(sizes_1mSZF)[9:10] <- c("F", "G")

```

```{r}
# make PGV data frame for PCA: bind by A:K

full_pgv <- bind_rows(sizes_1mSnoG, sizes_1mSZF, sizes_3mSnoG, sizes_3mSZF, sizes_3oSnoG, sizes_3oSZF, pgv_cream[4:5,], pgv_pellet[4:5,], pgv_serumUZ[4:5,], pgv_serumZF[4:5,])
full_pgv <- full_pgv[c(2:3,5:6,8:9,11:14,16:25),]
pgv.nms <- c("1mSnoG_1", "1mSnoG_2", "1mSZF_1", "1mSZF_2", "3mSnoG_1", "3mSnoG_2", "3mSZF_1", "3mSZF_2", "3oSnoG_1", "3oSnoG_2", "3oSZF_1", "3oSZF_2", "cream_1", "cream_2", "pellet_1", "pellet_2", "serumUZ_1", "serumUZ_2", "serumZF_1", "serumZF_2")

row.names(full_pgv) <- pgv.nms

pgv_pca <- full_pgv

pgv_pca$Kk <- NULL
pgv_pca <- pgv_pca[,c(1,2,3,4,5,9,10,6,7,8)]
pgv_pca["pellet_1","A"] <- 0 #no pellet obtainable therefore ==0
pgv_pca["pellet_2","A"] <- 0

pgv1_pca <- pgv_pca[5:20,1:9]
pgv1.pca <- prcomp(pgv1_pca, center = TRUE, scale. = TRUE)
autoplot(pgv1.pca, data = pgv1_pca, label=TRUE, loadings=TRUE)
```
indicates that data is correlated by one factor. The samples without salt don't correlate in their particle sizes with the data from the samples that were treated with the emulsifying salt mixture used herein. Hence, we can assume that the behaviour of the colloid is correlated to the behavior of the diluted, and centrifugationally treated model process cheese samples. 


```{r eval=FALSE, include=FALSE}
#pca algorithm for modellation of incomplete data, works with transposed full_pgv
pgv.pca <- estim_ncpPCA(pgv_pca,method.cv = "Kfold", verbose = FALSE)
res.comp <- imputePCA(pgv_pca, ncp = pgv.pca$ncp) # iterativePCA algorithm
pgv_imp <- res.comp$completeObs

pgv_imp.pca <- prcomp(pgv_imp, center = TRUE, scale = TRUE)
autoplot(pgv_imp.pca, data = pgv_imp, label=TRUE, loadings=TRUE)
```

```{r}
#PCA of protein concentration


```

